Hardware-Accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-06-04 paper.tex
Added results from workstation

The performance of each approach was measured by using a simple frame counter
showing the number of frames rendered in the previous second.  Multiple camera
angles and scene configurations were tried in order to expose strong and weak
points of the approaches.  The tests were run on two different machines with a
variety of operating systems (Linux, Mac OS X) and video cards (ATI, NVIDIA).
Table \ref{performance-table} shows the results.

\begin{table}
  \centering
  \begin{tabular}{ l l l }
    \toprule
    Approach & Macbook & Desktop \\
    \midrule
    Boolean AND with masking & 22 & 13 \\
    Boolean AND with XOR & 24 & 13 \\
    Slicing & 6 & 18 \\
    Optimized Slicing & 25 & 15 \\
    \bottomrule
  \end{tabular}
  \caption{Performance measurements}
  \label{performance-table}
\end{table}

Furthermore, a variety of sampling rates were used to determine how each
approach scales as the number of samples taken increases.  Figure
\ref{macbook-performance-chart} shows how the methods scale on a 2.2 GHz Intel
Core i7 Macbook Pro with an AMD Radeon HD 6750M video card.  Likewise figure
\ref{desktop-performance-chart} does so for an older 3.0 GHz Intel Pentium 4
Linux desktop with an NVIDIA GeForce 8500 GT video card.

@@

>>>>

The performance of each approach was measured by using a simple frame counter
showing the number of frames rendered in the previous second.  Multiple camera
angles and scene configurations were tried in order to expose strong and weak
points of the approaches.  The tests were run on three different machines with a
variety of operating systems (Linux, Mac OS X) and video cards (ATI, NVIDIA).
Table \ref{performance-table} shows the results.

\begin{table}
  \centering
  \begin{tabular}{ l l l l }
    \toprule
    Approach & Macbook & Desktop & Workstation\\
    \midrule
    Boolean AND with masking & 22 & 13 & 51 \\
    Boolean AND with XOR & 24 & 13 & 76 \\
    Slicing & 6 & 18 & 130 \\
    Optimized Slicing & 25 & 15 & 172 \\
    \bottomrule
  \end{tabular}
  \caption{Performance measurements}
  \label{performance-table}
\end{table}

Furthermore, a variety of sampling rates were used to determine how each
approach scales as the number of samples taken increases.  Figure
\ref{macbook-performance-chart} shows how the methods scale on a 2.2 GHz Intel
Core i7 Macbook Pro with an AMD Radeon HD 6750M video card.  Likewise figure
\ref{desktop-performance-chart} does so for an older 3.0 GHz Intel Pentium 4
Linux desktop with an NVIDIA GeForce 8500 GT video card.  Furthermore, figure
\ref{workstation-performance-chart} depicts the results for a newer 3.33 GHz
Intel Core i7 Linux workstation with an NVIDIA Quadro FX 5800 video card.

@@

\begin{figure}
\centering
\begin{tikzpicture}
\begin{axis}[
    title=3.33 GHz Intel Core i7 with Quadro FX 5800,
    xlabel=Samples,
    ylabel=Frames Per Second]
\addplot coordinates {
  (100, 51)
  (200, 28)
  (300, 19)
  (400, 14)
  (500, 11)
};
\addlegendentry{Depth-masking}
\addplot coordinates {
  (100, 76)
  (200, 39)
  (300, 27)
  (400, 23)
  (500, 17)
};
\addlegendentry{Boolean XOR}
\addplot coordinates {
  (100, 130)
  (200, 68)
  (300, 46)
  (400, 36)
  (500, 29)
};
\addlegendentry{Slicing (uniforms)}
\addplot coordinates {
  (100, 172)
  (200, 89)
  (300, 60)
  (400, 46)
  (500, 38)
};
\addlegendentry{Slicing (attributes)}
\end{axis}
\end{tikzpicture}
\caption{
Chart showing performance measurements as number of samples varies on an Intel
Core i7 system with a Quadro FX 5800 video card.  Here the difference between
the methods is more dramatic.  Both slicing methods handedly beat the
Boolean-based methods.
}
\label{workstation-performance-chart}
\end{figure}
